Entropy-SGD: Biasing Gradient Descent Into Wide Valleys

### 2017-01-13 doc/chaudhari.choromanska.ea.iclr17.tex
added a table

In Sec.~\ref{ss:expt:universality}, we discuss experiments that suggest that the characteristics of the energy landscape around local minimal accessible by SGD are universal to deep architectures.  This observation motivates the $\entropysgd$ algorithm considered in this paper and in Sec.~\ref{ss:expt:mnist} and~\ref{ss:expt:cifar}, we present experimental results on two standard image classification datasets, viz., MNIST and CIFAR-10.

@@

% {
% \renewcommand{\arraystretch}{1.3}
% \begin{table}[H]
% \centering
% \resizebox{0.8 \columnwidth}{!}
% {%
% \LARGE
% \begin{tabular}{p{8cm} c c r}
%     Model & Validation perplexity & Test perplexity & Time per effective epoch (s)\\  \hline
%     $\ptblstm$ (SGD) & $81.43 \pm 0.2$ & $78.6 \pm 0.26$ & $0$\\
%     $\ptblstm$ ($\entropysgd$) & $80.12 \pm 0.07$ & $77.66 \pm 0.17$ & $0$\\\hline
%     $\charlstm$ (Adam) & $1.224 \pm 0.008$ & $1.226 \pm 0.01$ & $0$\\
%     $\charlstm$ ($\entropyadam$) & $1.213 \pm 0.007$ & $1.217 \pm 0.005$ & $0$\\ \hline
% \end{tabular}
% }
% \caption{\small $\entropysgd$ on RNNs}
% \label{tab:rnns}
% \end{table}
% }

>>>>

In Sec.~\ref{ss:expt:universality}, we discuss experiments that suggest that the characteristics of the energy landscape around local minimal accessible by SGD are universal to deep architectures. We then present experimental results on two standard image classification datasets, viz. MNIST and CIFAR-10 and two datasets for text prediction, viz. PTB and the text of War and Peace. Table~\ref{tab:expts} summarizes the results of these experiments on deep networks.

@@

{
\setlength{\heavyrulewidth}{1.5pt}
\renewcommand{\arraystretch}{1.4}
\begin{table}[H]
\centering
\resizebox{0.9 \columnwidth}{!}
{
\large
\begin{tabular}{p{4cm} | c c | c c}
\toprule
    \rowcolor{gray!15} Model & \multicolumn{2}{c}{$\entropysgd$} & \multicolumn{2}{c}{SGD / Adam}\\
\toprule
    & Error (\%) / Perplexity & Epochs & Error (\%) / Perplexity & Epochs\\
    \rowcolor{gray!15} $\mnistfc$ & $1.37 \pm 0.03$ & $120$ & $1.39 \pm 0.03$ & $66$\\
    $\lenet$ & $0.5 \pm 0.01$ & $80$ & $0.51 \pm 0.01$ & $100$\\
    \rowcolor{gray!15} $\allcnn$ & $7.81 \pm 0.09$ & $115$ & $7.71 \pm 0.19$ & $180$\\
    $\ptblstm$ & $77.656 \pm 0.171$ & $25$ & $78.6 \pm 0.26$ & $55$\\
    \rowcolor{gray!15} $\charlstm$ & $1.217 \pm 0.005$ & $25$ & $1.226 \pm 0.01$ & $40$\\
\bottomrule
\end{tabular}
}
\caption{\small Experimental results: $\entropysgd$ vs. SGD / Adam}
\label{tab:expts}
\end{table}
}
